Visually pleasing knot projections

### 2022-06-15 inst/jma_knot.tex
move link discussion to appendix B also more futher work

The {\tt knotR} package allows the user to create rough diagrams of
knots using the inkscape suite of software, and subsequently polish up
such diagrams in terms of a customizable objective function using
numerical optimization techniques.

@@

\subsection{Some reflections on links}

@@

\clearpage
\section*{Appendix}

@@

@@

% ------------------------------------------------------------------------

% ------------------------------------------------------------------------
\end{document}
% ------------------------------------------------------------------------

>>>>

The {\tt knotR} package allows the user to create rough diagrams of
knots using the inkscape suite of software, and subsequently polish up
such diagrams in terms of a customizable objective function using
numerical optimization techniques.  The software makes a large number
of pleasing knot diagrams available to the community under the GPL.

One suggestion is that the software might be used in preference tests.
Subjects might be asked to state which of two knots [e.g. the two
  shown in Figure~\ref{figure_cca}] they find more attractive.  This
might allow us to make inferences about the mathematical basis for
aesthetics of knot diagrams---or perhaps to quantify some features of
subjective decision-making.

Further work might include adding functionality to deal with links,
although this is not straightforward, and a brief discussion is given
in Appendix B.

@@

@@

\clearpage
\section*{Appendix A: details and motivation for the badness functions}

@@

\section*{Appendix B: some reflections on links}

@@
